---
title: "In Dallas County"
format:
  html:
    includes:
      in_header: styles.css
                 header.html
---

```{r, Data Inputs}
#| include: FALSE
library(cpaltemplates)
library(tidycensus)
library(tidyverse)
library(rio)
library(sf)
library(googlesheets4)
library(DT)
library(grid)
library(gridExtra)

libDB <- "C:/Users/Michael/CPAL Dropbox/"

googlesheets4::gs4_auth(email = "michael@childpovertyactionlab.org")

# Load ggplot2
library(ggplot2)

# Create data
data <- data.frame(
  name=c("A","B","C","D","E") ,  
  value=c(0.8,0.7,0.4,0.2, 0.6)
  )
```

:::: {.columns}
::: {.column width="30%"}

```{=html}
<div class="section-container">
    <div class="section" style="text-align: center;">
        <i class="fas fa-people-group" style="font-size: 5em; color: #008097;"></i>
    </div>
    <div class="section-text">
        <b>123,123</b> potential eligible individuals are not enrolled in either EITC, SNAP, or WIC benefits, this constitutes 1 in 5 of all Dallas residents.
    </div>
</div>
```
:::
::: {.column width="5%"}
:::
::: {.column width="30%"}
```{=html}
<div class="section-container">
    <div class="section" style="text-align: center;">
        <i class="fas fa-baby" style="font-size: 5em; color: #008097;"></i>
    </div>
    <div class="section-text">
        <b>123,123</b> potential eligibles are children (11.1%), that's 1 in 3 of all children in Dallas County.
    </div>
</div>
```
:::
::: {.column width="5%"}
:::
::: {.column width="30%"}
```{=html}
<div class="section-container">
    <div class="section" style="text-align: center;">
        <i class="fas fa-money-bill-wave" style="font-size: 5em; color: #008097;"></i>
    </div>
    <div class="section-text">
        <b>$123,123.00</b> untapped annually in EITC, SNAP, WIC benefits can be sent back into the Dallas economy.
    </div>
</div>
```
:::
::::

#  What would Dallas look like if everyone eligible received their benefits?
:::: {.columns}
::: {.column width="50%"}
## Healthier Families
**<span style="font-size: 1.2em; color: #008097;">30% reduction in food insecurity</span>**

Here's a sentence telling us why food insecurity is bad.

**<span style="font-size: 1.2em; color: #008097;">35% reduction in overall healthcare costs</span>**

This sentence tells us that individuals are less burdened because of healthcare costs.

**<span style="font-size: 1.2em; color: #008097;">18% increase in high school completion</span>**

Now I'm telling you why it's important that higher high school completion rates leads to better social mobility.
:::
::: {.column width="50%"}
## Healthier Economy
**<span style="font-size: 1.2em; color: #ed018c;">$1,120,000 back into the Dallas County</span>** 

Benefits to sales, property ownership, and income taxes.

**<span style="font-size: 1.2em; color: #ed018c;">$1.79 in economic activity</span>** 

generated for every dollar in SNAP benefits.

**<span style="font-size: 1.2em; color: #ed018c;">13,560 new jobs</span>**

Are generated with additional $1B in SNAP benefits in the agriculture and transportation industries.
:::
::: {.column width="50%"}
```{r}
ggplot(data, aes(x=name, y=value)) + 
  geom_bar(stat = "identity",
           fill = palette_cpal_main[2]) +
  coord_flip() +
  labs(title = "Benefits Utilization($)",
       y = "",
       x = "") +
  theme_cpal_print()
```
:::
::: {.column width="50%"}
```{r}
ggplot(data, aes(x=name, y=value)) + 
  geom_bar(stat = "identity",
           fill = palette_cpal_main[5]) +
  coord_flip() +
  labs(title = "Benefits Utilization(Individuals)",
       y = "",
       x = "") +
  theme_cpal_print()
```
:::
# Here's a header telling me what WIC is.
::: {.column width="50%"}
Only **<span style="color: #ed018c;">12.3%</span>** of eligible participants receive WIC support in Dallas County. There is are additional **<span style="color: #ed018c;">123,123</span>** people eligible and **<span style="color: #ed018c;">$123,123</span>** untapped annually.

:::{.shadecontent}
{{< fa house-chimney size=lg title="Housing" >}} **Why this matters**: WIC (Special Supplemental Nutrition Program for Women, Infants, and Children) are proven to improve children's health outcome, **<span style="color: #ed018c;">reduce child malnutrition, and save an extra $1,863</span>** in health care expenditures a year.
:::

[Click here to learn more about resources and eligibilty.](https://quarto.org)
:::
::: {.column width="20%"}
```{r}
# Assuming 'data' is your dataframe and it has columns 'name' and 'value'
data %>%
  filter(name == "A") %>%
  mutate(remaining = 1 - value) %>%  # Calculate the remaining space
  ggplot(aes(x = name)) +
  geom_bar(aes(y = -value, fill = "your_value"), stat = "identity", width = 0.3) +
  geom_bar(aes(y = -remaining, fill = "remaining"), stat = "identity", width = 0.3) +
  scale_fill_manual(values = c(your_value = palette_cpal_main[5], remaining = palette_cpal_gray[1])) +
  geom_text(aes(y = -value, label = value), 
            vjust = -3, 
            size = 12) +  # Adjust 'size' as needed
  theme_void() +
  coord_cartesian(ylim = c(-1, 0)) +  # Adjust Y limits for inverted plot
  guides(fill = "none")  # Remove the legend
```
:::
::: {.column width="15%"}
```{=html}
<div class="section-container">
    <div class="section">
        <i class="fas fa-people-group" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <b>123,123 <br>Eligible Participants</b>
    </div>
</div>

<!-- Second section-container starts here -->
<div class="section-container">
    <div class="section">
        <!-- Modify the icon or style as needed -->
        <i class="fas fa-money-bill-wave" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <!-- Modify the text as needed -->
        <b>$456,456 <br>Estimated Dollars Available</b>
    </div>
</div>
```
:::
::: {.column width="15%"}
```{=html}
<div class="section-container">
    <div class="section">
        <i class="fas fa-people-group" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <b>123,123 <br>Actual Participants</b>
    </div>
</div>

<!-- Second section-container starts here -->
<div class="section-container">
    <div class="section">
        <!-- Modify the icon or style as needed -->
        <i class="fas fa-money-bill-wave" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <!-- Modify the text as needed -->
        <b>$456,456 <br>Dollars Allocated</b>
    </div>
</div>
```
:::
# Here's a header telling me what SNAP` is.
::: {.column width="50%"}
Only **<span style="color: #ffa13e;">12.3%</span>** of eligible participants receive WIC support in Dallas County. There is are additional **<span style="color: #ffa13e;">123,123</span>** people eligible and **<span style="color: #ffa13e;">$123,123</span>** untapped annually.

:::{.shadecontent}
{{< fa house-chimney size=lg title="Housing" >}} **Why this matters**: WIC (Special Supplemental Nutrition Program for Women, Infants, and Children) are proven to improve children's health outcome, **<span style="color: #ffa13e;">reduce child malnutrition, and save an extra $1,863</span>** in health care expenditures a year.
:::

[Click here to learn more about resources and eligibilty.](https://quarto.org)
:::
::: {.column width="20%"}
```{r}
# Assuming 'data' is your dataframe and it has columns 'name' and 'value'
data %>%
  filter(name == "A") %>%
  mutate(remaining = 1 - value) %>%  # Calculate the remaining space
  ggplot(aes(x = name)) +
  geom_bar(aes(y = -value, fill = "your_value"), stat = "identity", width = 0.3) +
  geom_bar(aes(y = -remaining, fill = "remaining"), stat = "identity", width = 0.3) +
  scale_fill_manual(values = c(your_value = palette_cpal_main[7], remaining = palette_cpal_gray[1])) +
  geom_text(aes(y = -value, label = value), 
            vjust = -3, 
            size = 12) +  # Adjust 'size' as needed
  theme_void() +
  coord_cartesian(ylim = c(-1, 0)) +  # Adjust Y limits for inverted plot
  guides(fill = "none")  # Remove the legend
```
:::
::: {.column width="15%"}
```{=html}
<div class="section-container">
    <div class="section">
        <i class="fas fa-people-group" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <b>123,123 <br>Eligible Participants</b>
    </div>
</div>

<!-- Second section-container starts here -->
<div class="section-container">
    <div class="section">
        <!-- Modify the icon or style as needed -->
        <i class="fas fa-money-bill-wave" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <!-- Modify the text as needed -->
        <b>$456,456 <br>Estimated Dollars Available</b>
    </div>
</div>
```
:::
::: {.column width="15%"}
```{=html}
<div class="section-container">
    <div class="section">
        <i class="fas fa-people-group" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <b>123,123 <br>Actual Participants</b>
    </div>
</div>

<!-- Second section-container starts here -->
<div class="section-container">
    <div class="section">
        <!-- Modify the icon or style as needed -->
        <i class="fas fa-money-bill-wave" style="font-size: 2em; color: #000000;"></i>
    </div>
    <div class="section-text">
        <!-- Modify the text as needed -->
        <b>$456,456 <br>Dollars Allocated</b>
    </div>
</div>
```
:::
::::

# About CPAL
CPAL is a Dallas-based nonprofit organization committed to cutting child poverty in
Dallas, Texas in half within a generation by (1) generating relevant data insights to break big problems into small, actionable ones, (2) facilitating cross-sector, collective action based on data insights, and (3) applying principles of human-centered design to solve problems in partnership with communities. One of CPAL’s five areas of focus is housing, and CPAL’s long-term aspiration is to ensure all Dallas families have access to stable housing without worry of an involuntary move.
